Lasso_RCI_Response

### 2024-04-02 Lasso_RCI_Response.Rmd
Results + tables and fig draft 1!

JT_DF

@@

#2. Left join data from the RCI dataset into the Mothership_post df
# Mothership_post <- left_join(Mothership_post,RCI_DF, by = join_by(ID1 == ID1)) |>
#   mutate(
#     Depression_Responder = ifelse(!is.na(class_RCI_dep), class_RCI_dep, NA),
#     Depression_Responder = as.factor(recode(Depression_Responder,
#                                             "1" = "2",
#                                             "2" = "2",
#                                             "3" = "1"
#     )),
#     Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
#     Depression_Responder = as.factor(recode(Depression_Responder,
#                                             "2" = "Non-Responder",
#                                             "1" = "Responder"
#     )),
#     Anxiety_Responder = ifelse(!is.na(class_RCI_anx), class_RCI_anx, NA),
#     Anxiety_Responder = as.factor(recode(Anxiety_Responder,
#                                          "1" = "2",
#                                          "2" = "2",
#                                          "3" = "1"
#     )),
#     Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, Anx_Responder)),
#     Anxiety_Responder = as.factor(recode(Anxiety_Responder,
#                                          "2" = "Non-Responder",
#                                          "1" = "Responder"
#     )),
#     RESPONDER_FIGS = as.factor(
#       ifelse(Anxiety_Responder == "Responder" | Depression_Responder == "Responder", "Responder",
#              ifelse(Anxiety_Responder == "Non-Responder" & Depression_Responder == "Non-Responder", "Non-Responder", NA)
#       ))) |>
#   filter(!is.na(RESPONDER_FIGS))

Mothership_post <- left_join(Mothership_post,JT_DF, by = join_by(ID1 == ID1)) |>
  mutate(
    Depression_Responder = ifelse(!is.na(class_JTRCI_dep), class_JTRCI_dep, NA),
    Depression_Responder = as.factor(recode(Depression_Responder,
                                            "1" = "2",
                                            "2" = "2",
                                            "3" = "1",
                                            "4" = "1",
                                            "5" = "1"
    )),
    Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
    Depression_Responder = as.factor(recode(Depression_Responder,
                                            "2" = "Non-Responder",
                                            "1" = "Responder"
    )),
    Anxiety_Responder = ifelse(!is.na(class_JTRCI_anx), class_JTRCI_anx, NA),
    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
                                         "1" = "2",
                                         "2" = "2",
                                         "3" = "1",
                                         "4" = "1",
                                         "5" = "1"
    )),
    Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, Anx_Responder)),
    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
                                         "2" = "Non-Responder",
                                         "1" = "Responder"
    ))) |>
  filter(
    !is.na(Anxiety_Responder),
    !is.na(Depression_Responder)
    )
```

@@

### Demographics information
- Table 1 Demographics By Response
- Table 2: Treatment information - What did treatment look like?
- Table 3: Scores on measures pre post change? 
    + I want to show the figure of pre-post change???
- Table 4: demographic breakdown
```{r}
Mothership_lasso <- Mothership_post |>
    filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(Anxiety_Responder),
    !is.na(Depression_Responder),
    CUXOS_pre >= 20,
    CUDOS_pre >= 20
  ) |>
  select( c(
    Anxiety_Responder, Depression_Responder,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, 
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, Delta_Anx_DC, CUDOS_pre, CUDOS_post, Delta_Dep_DC
  ))

@@

summary(Mothership_lasso$Anxiety_Responder)

# Vars_dep <- Mothership_lasso |>
#   select( c(
#     Depression_Responder,
#     # Demographics
#     Age_1,Some_College:Married,White, 
#     # Treatment info
#     IPT_track_1, Days_complete_1, Days_not_attended_1, 
#     # Disorders
#     Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
#     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
#     Current_Dx,
#     # Pre-Post stuff
#     CUDOS_pre,CUXOS_pre,
#     # RDQ
#     rdqPOST_coping:rdqPOST_wbs
#   ))

@@

## Vector of variables to summarize
table1_vars_anx <- c(colnames(Mothership_lasso)[-1])

## Vector of categorical variables that need transformation
catVars <- c("Some_College", "Female" , "Married", "White",
             "IPT_track_1","Anxiety_D", "Mood_D", "BPD_P" ,"Trauma_D","Substance_D" ,        
             "Psychotic_D", "Other", "Anxiety_C", "Mood_C" , "BPD_Co_C", "Trauma_C", 
             "Substance_C", "Other_C" , "No_Co"
             )
## Create a TableOne object
table1_tab_anx <- CreateTableOne(vars = table1_vars_anx, data = Vars_anx,strata ="Anxiety_Responder",  factorVars = catVars)
table1_tab_anx <- print(table1_tab_anx, formatOptions = list(big.mark = ","))
table1_tab_anx <- data.frame(table1_tab_anx)
write_csv(table1_tab_anx,"~/Downloads/table1_tab_anx.csv")
table1_tab_anx
### next gather info based upon depression

## Vector of variables to summarize
table1_vars_dep <- c(colnames(Vars_dep)[-1])

## Vector of categorical variables that need transformation
catVars <- c("Some_College", "Female" , "Married", "White",
             "IPT_track_1","Anxiety_D", "Mood_D", "BPD_P" ,"Trauma_D",        
             "Psychotic_D", "Other", "Anxiety_C", "Mood_C" , "BPD_Co_C", "Trauma_C", 
             "Substance_C", "Other_C" , "No_Co"
             )
## Create a TableOne object
table1_tab_dep <- CreateTableOne(vars = table1_vars_dep, data = Vars_dep,strata ="Depression_Responder",  factorVars = catVars)
table1_tab_dep <- print(table1_tab_dep, formatOptions = list(big.mark = ","))
table1_tab_dep <-data.frame(table1_tab_dep)
write_csv(table1_tab_dep,"~/Downloads/table1_tab_dep.csv")
table1_tab_dep

## lastly get the overal treatment breakdown
table1_gen <- CreateTableOne(vars = table1_vars_dep, data = Mothership_lasso,  factorVars = catVars)
table1_gen <- print(table1_gen, formatOptions = list(big.mark = ","))
table1_gen <-data.frame(table1_gen)
write_csv(table1_gen,"~/Downloads/table1_gen.csv")
table1_gen

@@

### Disorder Breakdowns
Here are some tables displaying info on the psychiatric disorders treated at the PHP
```{r}
# Disorders by treatment response
Dis_tab <- data.frame(table1::table1(~Disorder_Type + Current_Dx | Anxiety_Responder, 
                                     data = Mothership_lasso))
colnames(Dis_tab) = c("Variables","Anxiety Non Responder", "Anxiety Responder", "Total")

Dis_tab1 <- data.frame(table1::table1(~Disorder_Type + Current_Dx | Depression_Responder, 
                                     data = Mothership_lasso))
colnames(Dis_tab1) = c("Variables","Depression Non Responder", "Depression Responder", "Total")
Dis_tab <- cbind(Dis_tab1[,1:3],Dis_tab[,2:4])
Dis_tab

#Full demographic break down

co_dis_tab <- Mothership_lasso |>
  filter(
      !is.na(rdq_func_change),
      !is.na(rdq_pmh_change),
      !is.na(rdq_coping_change),
      !is.na(rdq_wbs_change)
  ) |>
  pivot_longer(
    cols = c("Anxiety_C","Mood_C","BPD_Co_C","Other_C", "Substance_C","Trauma_C", "No_Co"),
    names_to = 'Co Occuring',
    values_to = "Number"
  ) |>
  select(Disorder_treat, `Co Occuring`, Number) |>
  filter(Number != 0,
         !is.na(`Co Occuring`),
         !is.na(Disorder_treat),
         )

@@

Table 3: Correlation table?
- supplemental table 1: Full diagnostic breakdown of sample 
  + (co-occuring by Disorder)
```{r}
# Vars_dep <- Mothership_post |>
#   select( c(
#     # Demographics
#     Age_1,Some_College:Married,White, #Discharge,
#     # Treatment info
#     IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
#     # Disorders
#     Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
#     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
#     Current_Dx,
#     # Pre-Post stuff
#     CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
#     # RDQ
#     rdq_coping_change:rdq_wbs_change
#   ))
# 
# str(Vars_dep)
# 
# Vars_anx <- Mothership_post |>
#   select( c(
#     Anxiety_Responder,
#     # Demographics
#     Age_1,Some_College:Married,White, #Discharge,
#     # Treatment info
#     IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
#     # Disorders
#     Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
#     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
#     Current_Dx,
#     # Pre-Post stuff
#     CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
#     # RDQ
#     rdq_coping_change:rdq_wbs_change
#   ))

Vars_FULL <- na.omit(Vars_dep)

# install.packages("ggcorrplot")
library(ggcorrplot)
model.matrix(~0+., data=Vars_dep) %>% 
  cor(use="pairwise.complete.obs") %>% 
  ggcorrplot(show.diag=FALSE, type="lower", lab=TRUE, lab_size=2)

model.matrix(~0+., data=Vars_anx) %>% 
  cor(use="pairwise.complete.obs") %>% 
  ggcorrplot(show.diag=FALSE, type="lower", lab=TRUE, lab_size=2)

@@

### Final relaxed lasso- Depression
Minimum- 
```{r}
## install.packages("fuzzySim")
library(fuzzySim) ## For FDR adjusted p values
library(broom) # for tidy regression output
```

```{r}
## min model
  glm_min_dep <-
            glm(
      #Outcome varaible
        Depression_Responder ~
      # predictors
        Days_complete_1 + Days_not_attended_1 + Mood_C + CUDOS_pre +
        CUXOS_pre + rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
      #data
        data = Vars_dep,
      # type of regression : logistic = binary / binomial
        family = "binomial")

@@

Vars_anx <- Mothership_lasso_anx |>
  select( c(
    Anxiety_Responder,
    # Demographics
    Age_1,Some_College:Married,White, 
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, 
    # Disorders
    Anxiety_D, Mood_D, BPD_P,    Trauma_D, 
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs
  ))

@@

## min model
  glm_min_anx <-  
      glm(
      #Outcome varaible
        Anxiety_Responder ~ 
      # predictors
        Age_1 + Married + Days_complete_1 + Days_not_attended_1 +
        Anxiety_D + Trauma_D +  BPD_Co_C + 
        rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
      #data
      data = Vars_anx, 
      # type of regression : logistic = binary / binomial
      family = "binomial")

@@

## 1se model
  glm_1se_anx <-  
      glm(
      #Outcome varaible
        Anxiety_Responder ~ 
      # predictors
        Days_not_attended_1 + CUXOS_pre + rdqPOST_coping + rdqPOST_pmh + rdqPOST_wbs,
      #data
      data = Vars_anx, 
      # type of regression : logistic = binary / binomial
      family = "binomial")
# Summary of the model

@@

# Left join the FDR adjusted p.value
FP.1se.anx <- left_join(FP.1se.anx,ADJ.p.values.1se.anx, by = join_by(p.values == p.value))
FP.1se.anx$type = c("Anxiety")
FP.1se.anx
```

@@

FP_anx <- read_csv("~/Downloads/FP.min.anx")

@@

FP_anx$Variable = c(
                    "Age", "Married", "Days Completed", "Days Not Attended", 
                    "Anxiety Disorder", "Trauma Disorder", "Co-Occuring BPD",
                    "Coping Ability", "Positive Mental Health", "Functioning", 
                    "Sense of Well Being"
                    )

>>>>

View(JT_DF)

@@

#2. Left join data from the RCI dataset into the Mothership_post df
# Mothership_post <- left_join(Mothership_post,RCI_DF, by = join_by(ID1 == ID1)) |>
#   mutate(
#     Depression_Responder = ifelse(!is.na(class_RCI_dep), class_RCI_dep, NA),
#     Depression_Responder = as.factor(recode(Depression_Responder,
#                                             "1" = "2",
#                                             "2" = "2",
#                                             "3" = "1"
#     )),
#     Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
#     Depression_Responder = as.factor(recode(Depression_Responder,
#                                             "2" = "Non-Responder",
#                                             "1" = "Responder"
#     )),
#     Anxiety_Responder = ifelse(!is.na(class_RCI_anx), class_RCI_anx, NA),
#     Anxiety_Responder = as.factor(recode(Anxiety_Responder,
#                                          "1" = "2",
#                                          "2" = "2",
#                                          "3" = "1"
#     )),
#     Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, Anx_Responder)),
#     Anxiety_Responder = as.factor(recode(Anxiety_Responder,
#                                          "2" = "Non-Responder",
#                                          "1" = "Responder"
#     )),
#     RESPONDER_FIGS = as.factor(
#       ifelse(Anxiety_Responder == "Responder" | Depression_Responder == "Responder", "Responder",
#              ifelse(Anxiety_Responder == "Non-Responder" & Depression_Responder == "Non-Responder", "Non-Responder", NA)
#       ))) |>
#   filter(!is.na(RESPONDER_FIGS))
```

JT Numbers
```{r}
# Mothership_post <- left_join(Mothership_post,JT_DF, by = join_by(ID1 == ID1)) |>
#   mutate(
#     Depression_Responder = ifelse(!is.na(class_JTRCI_dep), class_JTRCI_dep, NA),
#     Depression_Responder = as.factor(recode(Depression_Responder,
#                                             "1" = "2",
#                                             "2" = "2",
#                                             "3" = "1",
#                                             "4" = "1",
#                                             "5" = "1"
#     )),
#     Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
#     Depression_Responder = as.factor(recode(Depression_Responder,
#                                             "2" = "Non-Responder",
#                                             "1" = "Responder"
#     )),
#     Anxiety_Responder = ifelse(!is.na(class_JTRCI_anx), class_JTRCI_anx, NA),
#     Anxiety_Responder = as.factor(recode(Anxiety_Responder,
#                                          "1" = "2",
#                                          "2" = "2",
#                                          "3" = "1",
#                                          "4" = "1",
#                                          "5" = "1"
#     )),
#     Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, Anx_Responder)),
#     Anxiety_Responder = as.factor(recode(Anxiety_Responder,
#                                          "2" = "Non-Responder",
#                                          "1" = "Responder"
#     ))) |>
#   filter(
#     !is.na(Anxiety_Responder),
#     !is.na(Depression_Responder)
#     )
```

RCI numbers
```{r}
Mothership_post <- left_join(Mothership_post,RCI_DF, by = join_by(ID1 == ID1)) |>
  mutate(
    Depression_Responder = ifelse(!is.na(class_RCI_dep), class_RCI_dep, NA),
    Depression_Responder = as.factor(recode(Depression_Responder,
                                            "1" = "2",
                                            "2" = "2",
                                            "3" = "1",
                                            "4" = "1",
                                            "5" = "1"
    )),
    Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
    Depression_Responder = as.factor(recode(Depression_Responder,
                                            "2" = "Non-Responder",
                                            "1" = "Responder"
    )),
    Anxiety_Responder = ifelse(!is.na(class_RCI_anx), class_RCI_anx, NA),
    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
                                         "1" = "2",
                                         "2" = "2",
                                         "3" = "1",
                                         "4" = "1",
                                         "5" = "1"
    )),
    Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, Anx_Responder)),
    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
                                         "2" = "Non-Responder",
                                         "1" = "Responder"
    ))) |>
  filter(
    !is.na(Anxiety_Responder),
    !is.na(Depression_Responder)
    )
```

@@

### Demographics information
- Table 1 Demographics By Response
- Table 2: Treatment information - What did treatment look like?
- Table 3: Scores on measures pre post change? 
    + I want to show the figure of pre-post change???
- Table 4: demographic breakdown
```{r}
Mothership_lasso <- Mothership_post |>
    filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(Anxiety_Responder),
    !is.na(Depression_Responder),
    CUXOS_pre >= 20,
    CUDOS_pre >= 20
  ) |>
  select( c(
    Anxiety_Responder, Depression_Responder,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, Delta_Anx_DC, CUDOS_pre, CUDOS_post, Delta_Dep_DC
  ))

@@

@@

## Vector of variables to summarize
table1_vars_anx <- c("Anxiety_Responder",colnames(Mothership_lasso)[-1:-3])
table1_vars_anx <- table1_vars_anx[1:28]

colnames(Mothership_lasso)[-1]
## Vector of categorical variables that need transformation
catVars <- c("Some_College", "Female" , "Married", "White",
             "IPT_track_1","Anxiety_D", "Mood_D", "BPD_P" ,"Trauma_D","Substance_D" ,        
             "Psychotic_D", "Other", "Anxiety_C", "Mood_C" , "BPD_Co_C", "Trauma_C", 
             "Substance_C", "Other_C" , "No_Co"
             )

## Create a TableOne object
table1_tab_anx <- CreateTableOne(vars = table1_vars_anx, data = Mothership_lasso,strata ="Anxiety_Responder",  factorVars = catVars)
table1_tab_anx <- print(table1_tab_anx, formatOptions = list(big.mark = ","))
table1_tab_anx <- data.frame(table1_tab_anx)
write_csv(table1_tab_anx,"~/Downloads/table1_tab_anx.csv")
table1_tab_anx
### next gather info based upon depression

## Vector of variables to summarize
table1_vars_dep <- c("Depression_Responder",colnames(Mothership_lasso)[-1:-3])
table1_vars_dep <- table1_vars_dep[1:28]

## Create a TableOne object
table1_tab_dep <- CreateTableOne(vars = table1_vars_dep, data = Mothership_lasso,strata ="Depression_Responder",  factorVars = catVars)
table1_tab_dep <- print(table1_tab_dep, formatOptions = list(big.mark = ","))
table1_tab_dep <-data.frame(table1_tab_dep)
write_csv(table1_tab_dep,"~/Downloads/table1_tab_dep.csv")
table1_tab_dep

## Vector of variables to summarize
table1_vars_gen <- c(colnames(Mothership_lasso)[-1:-3])
table1_vars_gen<- table1_vars_gen[1:27]

## lastly get the overal treatment breakdown
table1_gen <- CreateTableOne(vars = table1_vars_gen, data = Mothership_lasso,  factorVars = catVars)
table1_gen <- print(table1_gen, formatOptions = list(big.mark = ","))
table1_gen <-data.frame(table1_gen)
write_csv(table1_gen,"~/Downloads/table1_gen.csv")
table1_gen

mean(Mothership_lasso$CUDOS_pre)
sd(Mothership_lasso$CUDOS_pre)
mean(Mothership_lasso$CUDOS_post)
sd(Mothership_lasso$CUDOS_post)

@@

### Disorder Breakdowns
Here are some tables displaying info on the psychiatric disorders treated at the PHP
```{r}
# Disorders by treatment response
Dis_tab <- data.frame(table1::table1(~Disorder_treat + Current_Dx | Anxiety_Responder, 
                                     data = Mothership_lasso))
colnames(Dis_tab) = c("Variables","Anxiety Non Responder", "Anxiety Responder", "Total")

Dis_tab1 <- data.frame(table1::table1(~Disorder_treat + Current_Dx | Depression_Responder, 
                                     data = Mothership_lasso))
colnames(Dis_tab1) = c("Variables","Depression Non Responder", "Depression Responder", "Total")
Dis_tab <- cbind(Dis_tab1[,1:3],Dis_tab[,2:4])
Dis_tab

#Full demographic break down
dim(Mothership_lasso)

co_dis_tab <- Mothership_lasso |>
  pivot_longer(
    cols = c("Anxiety_C","Mood_C","BPD_Co_C","Other_C", "Substance_C","Trauma_C", "No_Co"),
    names_to = 'Co Occuring',
    values_to = "Number"
  ) |>
  select(Disorder_treat, `Co Occuring`, Number) |>
  filter(Number != 0,
         !is.na(`Co Occuring`),
         !is.na(Disorder_treat),
         )

@@

Table 3: Correlation table?
- supplemental table 1: Full diagnostic breakdown of sample 
  + (co-occuring by Disorder)
```{r}

Vars_dep <- Mothership_lasso |>
  select( c(
    Depression_Responder,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs  
    ))

Vars_anx <- Mothership_lasso |>
  select( c(
    Anxiety_Responder,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs  
  ))

#Make a correlation table???

# install.packages("ggcorrplot")
# library(ggcorrplot)
# model.matrix(~0+., data=Mothership_lasso) %>% 
#   cor(use="pairwise.complete.obs") %>% 
#   ggcorrplot(show.diag=FALSE, type="lower", lab=TRUE, lab_size=2)
# 
# model.matrix(~0+., data=Vars_anx) %>% 
#   cor(use="pairwise.complete.obs") %>% 
#   ggcorrplot(show.diag=FALSE, type="lower", lab=TRUE, lab_size=2)

@@

### Final relaxed lasso- Depression
Minimum- 
```{r}
## install.packages("fuzzySim")
library(fuzzySim) ## For FDR adjusted p values
library(broom) # for tidy regression output

## min model
  glm_min_dep <-
            glm(
      #Outcome varaible
        Depression_Responder ~
      # predictors
        Days_complete_1 + Days_not_attended_1 + Mood_C + CUDOS_pre +
        CUXOS_pre + rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
      #data
        data = Vars_dep,
      # type of regression : logistic = binary / binomial
        family = "binomial")

@@

Vars_anx <- Mothership_lasso_anx |>
  select( c(
    Anxiety_Responder,
    # Demographics
    Age_1,Some_College:Married,White, 
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, 
    # Disorders
    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs
  ))

@@

## min model
  glm_min_anx <-  
      glm(
      #Outcome varaible
        Anxiety_Responder ~ 
      # predictors
        Age_1 + Married + Days_complete_1 + Days_not_attended_1 +
        Anxiety_D + Trauma_D +  BPD_Co_C + CUXOS_pre +
        rdqPOST_coping + rdqPOST_pmh + rdqPOST_func,
      #data
      data = Vars_anx, 
      # type of regression : logistic = binary / binomial
      family = "binomial")

@@

## 1se model
  glm_1se_anx <-  
      glm(
      #Outcome varaible
        Anxiety_Responder ~ 
      # predictors
        Days_complete_1 + Days_not_attended_1 + Anxiety_D +CUXOS_pre + rdqPOST_coping + rdqPOST_pmh + rdqPOST_func,
      #data
      data = Vars_anx, 
      # type of regression : logistic = binary / binomial
      family = "binomial")
# Summary of the model

@@

# Left join the FDR adjusted p.value
FP.1se.anx <- left_join(FP.1se.anx,ADJ.p.values.1se.anx, by = join_by(p.values == p.value))
FP.1se.anx$type = c("Anxiety")
FP.1se.anx

write_csv(FP.1se.anx, "~/Downloads/FP.1se.anx")
```

@@

FP_anx <- read_csv("~/Downloads/FP.min.anx")
# FP_anx <- read_csv("~/Downloads/FP.1se.anx")

@@

FP_anx$Variable = c(
                    "Age", "Unmarried", "Days Completed", "Days Not Attended",
                    "Anxiety Disorder", "Trauma Disorder", "Co-Occuring BPD",
                    "CUXOS Pre-Score",
                    "Coping Ability", "Positive Mental Health", "Functioning"
                    )
# FP_anx$Variable = c(                      
#                     "Days Completed","Days Not Attended","Anxiety Disroder","CUXOS Pre-score",
#                     "Coping Ability","Positive Mental Health", "Functioning"   
#                     )
